Latex Tikz Examples, Discrete and Continuous Strategy Trees

### 2020-02-18 _other/tikz/tree/fs_tikz_gametree.tex
game tree theta phi

% url package
\usepackage{hyperref}
\usepackage{subcaption}

@@

% C Level 2 Node (child nodes)
% C.1 First child node, left
child{
    % C.1.a Node line color
    [red]
    % C.1.b Node dot
    node(1)[solid node, label=below:{red dot}]{}
    % C.1.c now go to edge
    edge from parent
        % C.1.c Node along edge
        node[sloped, above, black, text width=3cm]{Minimum Choice showing up along this red line}
    }
% C.2 Middle Child node, do not show line, invisible
child{
    % Main node of level 2 middle node, same y-axis height as node left and right
    % Y-shift to move level 3 child node lower
    [purple] node(2)[solid node, xshift=30, yshift=-50, label=right:{hello}]{}
    % D.1 Left level 3 (from middle level 2)
    child{
        [black]
        node[hollow node,label=below:{$(a,b)$}]{}
        edge from parent
            node[left]{$C$}
        }
    child{
        [black]
        node[hollow node,label=below:{$(c,d)$}]{}
        edge from parent
            node[right]{$D$}
        }
    edge from parent
        %note that you need to adjust the yshift if you change the level distance
        node[left, black, xshift=-5, yshift=0, text width = 1mm]{$\alpha$\\$\beta$\\$\sigma$}
    }
child{
    [black]
    node(3)[solid node, label=right:{hi there}, green]{}
    edge from parent
        node[right, xshift=0, yshift=15, text width=2cm]{Some text for this edge}
    };
% information set
\draw[dashed, bend right]
    (1) to (3);
\draw[dashed, bend left, line width=0.5mm, blue]
    (0) to
        node[right, text width=1.25cm, xshift=5, yshift=-10]
            {\tiny{label right of blue dashed line}}
        (2);
\end{tikzpicture}
\end{center}

@@

\def\famm{5mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
% B Level 1 point
\node(0)[solid node,label=left:{$P1$}]{}
[grow=right]
child{ 
    [black] node(11)[]{}
}
child{
    [grow=right]
    child{
        [black] node(21)[]{}
    }
    child{
        [grow=right]
        child
        child
        child
        child
    }
    child{
        [black] node(23)[]{}
    }
}
child{
    [black] node(13)[]{}
};
% information set
\draw[dashed, bend right]
    (11) to (13);
\draw[dashed, bend right]
    (21) to (23);
\end{tikzpicture}
\end{center}

@@

\def\famm{5mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
% B Level 1 point
\node(0)[solid node,label=left:{$P1$}]{}
[grow=right]
child{ 
    [black] node(11)[]{}
}
child{
    [grow=right]
    [white] node(12)[solid node, xshift=7.5, yshift=0]{}
    child{
        [black] node(21)[]{}
    }
    child{
        [grow=right]
        [white] node(22)[solid node, xshift=7.5, yshift=0]{}
        child {
            [black] node(31)[]{}
        }
        child{
            [black] node(32)[]{}
        }
        child{
            [black] node(33)[]{}   
        }
        child{
            [black] node(34)[]{}
        }
    }
    child{
        [black] node(23)[]{}
    }
}
child{
    [black] node(13)[]{}
};
% information set
\draw[dashed, bend right]
    (11) to (13);
\draw[dashed, bend right]
    (21) to (23);
\draw[dotted, line width=0.35mm]
    (0) to (12);
\draw[dotted, line width=0.35mm]
    (12) to (22);
\end{tikzpicture}
\end{center}

>>>>

% url package
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{relsize} % make some math large
\usepackage{bm} % make some math bold

@@

% C Level 2 Node (child nodes)
% C.1 First child node, left
child{
    % C.1.a Node line color
    [red]
    % C.1.b Node dot
    node(1)[solid node, label=below:{red dot}]{}
    % C.1.c now go to edge
    edge from parent
        % C.1.c Node along edge
        node[sloped, above, black, text width=3cm]{Minimum Choice showing up along this red line}
    }
% C.2 Middle Child node, do not show line, invisible
child{
    % Main node of level 2 middle node, same y-axis height as node left and right
    % Y-shift to move level 3 child node lower
    [red]  % this is the style of the line middle line
        node(2)[solid node, xshift=30, yshift=-50, label=right:{hello}]{} % this is the style of the middle point that would have matched up the middle line        
    % D.1 Left level 3 (from middle level 2)
    child{
        [black]
        node[hollow node,label=below:{$(a,b)$}]{}
        edge from parent
            node[left]{$C$}
        }
    child{
        [black]
        node[hollow node,label=below:{$(c,d)$}]{}
        edge from parent
            node[right]{$D$}
        }
    edge from parent
        % draw none here prevents the middle line extending rom P1 to hello to be drawn
        [draw=none]
        %note that you need to adjust the yshift if you change the level distance
        node[left, black, xshift=-5, yshift=0, text width = 1mm]{$\alpha$\\$\beta$\\$\sigma$}
    }
child{
    [black]
    node(3)[solid node, label=right:{hi there}, green]{}
    edge from parent
        node[right, xshift=0, yshift=15, text width=2cm]{Some text for this edge}
    };
% information set
\draw[dashed, bend right]
    (1) to (3);
\draw[dashed, bend left, line width=0.5mm, blue]
    (0) to
        node[right, text width=1.25cm, xshift=5, yshift=-10]
            {\tiny{label right of blue dashed line}}
        (2);
\end{tikzpicture}
\end{center}

@@

\def\famm{5mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
% B Level 1 point
\node(0)[solid node,label=left:{$P1$}]{}
[grow=right]
child{ 
    [black] node(11)[]{}
}
child{
    [grow=right]
    child{
        [blue] node(21)[]{}
    }
    child{
        [grow=right]
        child
        child
        child
        child
    }
    child{
        [red] node(23)[]{}
    }
}
child{
    [red] node(13)[]{}
};
% information set
\draw[dashed, bend right]
    (11) to (13);
\draw[dashed, bend right]
    (21) to (23);
\end{tikzpicture}
\end{center}

@@

\def\famm{5mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]
\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
% B Level 1 point
\node(0)[solid node,label=left:{$P1$}]{}
[grow=right]
child{ 
    [black] node(11)[]{}
}
child{
    [grow=right]
    [white] node(12)[solid node, xshift=7.5, yshift=0]{}
    child{
        [black] node(21)[]{}
    }
    child{
        [grow=right]
        [white] node(22)[solid node, xshift=7.5, yshift=0]{}
        child {
            [black] node(31)[]{}
        }
        child{
            [black] node(32)[]{}
        }
        child{
            [black] node(33)[]{}   
        }
        child{
            [black] node(34)[]{}
        }
    }
    child{
        [black] node(23)[]{}
    }
}
child{
    [black] node(13)[]{}
};
% information set
\draw[dashed, bend right]
    (11) to (13);
\draw[dashed, bend right]
    (21) to (23);
\draw[dotted, line width=0.35mm]
    (0) to (12);
\draw[dotted, line width=0.35mm]
    (12) to (22);
\end{tikzpicture}
\end{center}

\subsection{Spanning Multi--Tree with Text as a part of Timeline}

Two spanning continuous choices, with text on boundary, clear descriptions. inside of what choices are made. Then inset this as a part of a longer timeline.

\subsubsection{Two Nodes and Text Along Edges}

\def\famm{13mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]
\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
% B Level 1 point
\node(0)[solid node, % solid node gives fist (left to right) black dot
         label=left:{
            $\textcolor{black}{\mathlarger{\mathlarger{\mathlarger{\bm{\phi}}}}}$
             }]{}
[grow=right]
child{ 
    [black] node(11)[]{}
    edge from parent
            node[sloped, below, black]{$\phi=0$}
}
child{
    [grow=right]
    % The starting node for theta
    node(12)[solid node, xshift=16, yshift=0, % solid node gives second (left to right) black dot
                     label=left:{
                        $\textcolor{black}{\mathlarger{\mathlarger{\mathlarger{\bm{\theta}}}}}$
                     }]{}
    % Draw the theta branches
        child{
            [red] node(21)[]{}
            edge from parent
                node[sloped, below, black]{$\theta=0$}
        }
        child{
            [white] node(22)[xshift=16, yshift=0]{}        
            edge from parent
                [draw=none] % prevents a line to be drawn from phi to phi
                node[above, black, xshift=7]{$k' = \theta \cdot \Lambda$}
                node[below, black, xshift=10]{$b' = \Lambda - k'$}    
        }
        child{
            [black] node(23)[]{}
            edge from parent
                node[sloped, above, black]{$\theta=1$}
        }
    edge from parent
        [draw=none] % prevents a line to be drawn from phi to phi
        % node[above, black, yshift=-55]{$c = \phi \cdot \Gamma$}
        % node[below, black, yshift=-55]{$\Lambda = \left(1-\phi\right) \cdot \Gamma$}
        node[above, black, xshift=4]{$c = \phi \cdot \Gamma$}
        node[below, black, xshift=4]{$\Lambda = \Gamma - c$}
        }
child{
    [red] node(13)[]{}
    edge from parent
            node[sloped, above, black]{$\phi=1$}
};
% information set
\draw[dashed, bend right]
    (11) to (13);
\draw[dashed, bend right]
    (21) to (23);
\end{tikzpicture}
\end{center}

% child{
%     % C.1.a Node line color
%     [red]
%     % C.1.b Node dot
%     node(1)[solid node, label=below:{red dot}]{}
%     % C.1.c now go to edge
%     edge from parent
%         % C.1.c Node along edge
%         node[sloped, above, black, text width=3cm]{Minimum Choice showing up along this red line}
%     }
